DATA 621 – Business Analytics and Data Mining: Homework #1

### 2020-09-09 HW1/HW1_BP.rmd
Add files via upload

@@

train_set <- read.csv('data/moneyball-training-data.csv')
eval_set <- read.csv('data/moneyball-evaluation-data.csv')

@@

>>>>

```{r}
library(dplyr)
library(reshape2)
library(ggplot2)
```

@@

train_set <- read.csv('/Users/Bryan/Documents/Data 621/HW 1/moneyball-training-data.csv')
eval_set <- read.csv('/Users/Bryan/Documents/Data 621/HW 1/moneyball-evaluation-data.csv')

@@

# Data Transformation

```{r}
train_set <- train_set %>%
  filter(TARGET_WINS >= 20 & TARGET_WINS <= 125 & TEAM_BATTING_H <= 1880 & TEAM_BATTING_2B >= 115 & TEAM_BATTING_2B <= 380 & TEAM_BATTING_BB >= 300 & TEAM_BATTING_BB <= 870 & TEAM_BATTING_SO <= 1540 & TEAM_PITCHING_HR <= 255 & TEAM_PITCHING_SO <= 1450)
train_set[train_set == 0] <- NA
```

```{r}
sub = melt(train_set)
ggplot(sub, aes(x = value)) + geom_density() + facet_wrap(~ variable, scales = 'free')
```

# Build Model

```{r}
model1 <- lm(TARGET_WINS ~ ., train_set)
summary(model1)
```

```{r}
model2 <- lm(TARGET_WINS ~ TEAM_BATTING_H + TEAM_BATTING_HR + TEAM_BATTING_SO + TEAM_PITCHING_HR, train_set)
summary(model2)
```
